Downscale t2m for KSS

### 2016-10-18 KSS/ds-t2m4KSS.Rmd
update from VGL

```{r predictand-data}
if (!file.exists('t2m.nordic.rda')) {
  ss <- select.station(param='t2m',lon=c(5,30),lat=c(55,72),src='ecad',nmin=50)
  X <- station(ss)
  save(X,file='t2m.nordic.rda')
} else load('t2m.nordic.rda')
```

```{r}
## Only use the most recent 66 years 
X <- subset(X,it=c(1950,2015))
## Remove records with many missing datapoints
nv <- apply(coredata(X),2,'nv')
```

@@

param <- 't2m'
FUN <- 'mean'
reanalysis <- 'air.mon.mean.nc'
lon=c(0,100); lat=c(65,90)

if (param=='precip') FUNX <- 'C.C.eq' else FUNX <- 'mean'

## Get the predictand -> Y
if (!exists('Y')) {
  load(paste(param,'.nordic.rda',sep=''))
}

@@

  ## Carry out the downscaling:
  if (!file.exists(paste('dse.kss.t2m.rcp45.',it,'.rda',sep=''))) {
    Z <- downscale(Y,predictor,it,param,FUN=FUN,FUNX=FUNX,lon=lon,lat=lat)
    save(file=paste('dse.kss.t2m.rcp45.',it,'.rda',sep=''),Z)
  }

@@

  if (!file.exists(paste('dse.kss.t2m.rcp26.',it,'.rda',sep=''))) {
    Z <- downscale(Y,predictor,it,param,rcp='rcp26',
                                    FUN=FUN,FUNX=FUNX,lon=lon,lat=lat)
    save(file=paste('dse.kss.t2m.rcp26.',it,'.rda',sep=''),Z)
  }

@@

  if (!file.exists(paste('dse.kss.t2m.rcp85.',it,'.rda',sep=''))) {
    Z <- downscale(Y,predictor,it,param,rcp='rcp85',
                                    FUN=FUN,FUNX=FUNX,lon=lon,lat=lat)
    save(file=paste('dse.kss.t2m.rcp85.',it,'.rda',sep=''),Z)
  }
}
print('--- Completed downscaling ---')
```

>>>>

```{r predictand-data}
if (!file.exists('t2m.nordic.rda')) {
  ss <- select.station(param='tg',lon=c(5,30),lat=c(55,72),src='ecad',nmin=50)
  Y <- station(ss)
  save(Y,file='t2m.nordic.rda')
} else load('t2m.nordic.rda')
```

```{r}
## Only use the most recent 66 years 
Y <- subset(Y,it=c(1960,2015))
## Remove records with many missing datapoints
nv <- apply(coredata(Y),2,'nv')
Y <- subset(Y,is=nv > 14000)
```

@@

FUN <- 'mean'
reanalysis <- 'air.mon.mean.nc'
lon=c(-30,30); lat=c(50,75)
FUNX <- 'mean'
verbose=TRUE

@@

  ## Carry out the downscaling:
  if (!file.exists(paste('dse.kss.t2m.rcp45.',it,'.rda',sep=''))) {
    Z <- downscale(Y,predictor,it,param,FUN=FUN,FUNX=FUNX,lon=lon,lat=lat,verbose=verbose)
    save(file=paste('dse.kss.t2m.rcp45.',it,'.rda',sep=''),Z)
  }

@@

  if (!file.exists(paste('dse.kss.t2m.rcp26.',it,'.rda',sep=''))) {
    Z <- downscale(Y,predictor,it,param,rcp='rcp26',
                                    FUN=FUN,FUNX=FUNX,lon=lon,lat=lat,verbose=verbose)
    save(file=paste('dse.kss.t2m.rcp26.',it,'.rda',sep=''),Z)
  }

@@

  if (!file.exists(paste('dse.kss.t2m.rcp85.',it,'.rda',sep=''))) {
    Z <- downscale(Y,predictor,it,param,rcp='rcp85',
                                    FUN=FUN,FUNX=FUNX,lon=lon,lat=lat,verbose=verbose)
    save(file=paste('dse.kss.t2m.rcp85.',it,'.rda',sep=''),Z)
  }
}
print('--- Completed downscaling ---')
```
